---
title: "Eating Out"
author: "Eden Williams"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Methods

response variable is categorical: did you dine out last week? yes or no?

explanatory variable is race, which is also a categorical variable. So we will use cat~cat

Inference: chi-squared and fisher exact tests

# Descriptive Summaries 

## Graphical Summary 

### barchart


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

Based upon the graph above it seems that race does determine the frequency in which some one eats out. Based on the graph it seems that white people eat out the most. 

## Numerical Summary 

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

This table shows that of all the races white people tend to eat out the most. Which again shows that race does play a role in the frequency in which one eats out.


