---
title: "Eating Out"
author: "Eden Williams"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Methods

response variable is categorical: did you dine out last week? yes or no?

explanatory variable is race, which is also a categorical variable. So we will use cat~cat

Inference: chi-squared and fisher exact tests

# Descriptive Summaries 

## Graphical Summary 

### barchart


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

Based upon the graph above it seems that race does determine the frequency in which some one eats out. Based on the graph it seems that white people eat out the most. 

## Numerical Summary 

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

This table shows that of all the races white people tend to eat out the most. Which again shows that race does play a role in the frequency in which one eats out.


# Results 

## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Based on the chi-squared test we can see that the frequency in which someone eats out is linked to race.The p-value is 0.000002287 which means that we can reject the null hypothesis. 


```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```
Based upon the chart above we see that white people are more likely to eat out than the other races. Based upon the odds ratio it seems that white people are twice as likely to eat out when compared to black folks and almost twice as likely when it comes to other races as well.We don't have enough statistical data between black folks and other races to conclude that there is much of a difference between them when it comes to eating out since out p-value is 0.5993.
